---
title: "Troubleshooting Workshop"
author: "Christian Staal Bruun Overgaard"
date: "Fall, 2022"
output: html_document
---

## Import data

What's wrong? Three things.

```{r import}
sw <- read_csv(https://raw.githubusercontent.com/cstaal88/tutorials/ec0748214109e4a31991332a85d84ccba78d06f6/star_wars_characters.csv
```

Google this: R Error: unexpected '/' in


### Remember to import libraries

```{r import_again}
library(tidyverse)
library(jainitor)
```

## Clean names

(What's wrong here? 3 issues!)

```{r clean_names}
sw-clean <- sw |> clean_names())
```

Google this: R could not find function


## Glimpse

```{r glimpse}
glimpse(sw-clean) #what's wrong?
```


## Select certain variables

```{r select}
sw_birthday_species <- sw_clean
  |> Select(name, birthday, species) #
```

(Hint for cell above: Which line? Capital s?)

## Filtering

(Spot 3 mistakes)

```{r filter}
sw_clean |> filter(species = human) 
```

```{r filter2}
sw_clean |> filter(hair color == "bronw") # what's wrong?

sw_clean |> filter(hair_color == "bronw") # 0 rows? why?
```

## Multiple pipes

Find the frequency of each eye color.

```{r}
sw_clean |> # and then ...
  group_by(eye_color) 
  |> summarize(total = n() |> #TWO issues here
  arrange(desc(total))
```

### Solution with comments

```{r}
sw_clean |> # and then ...
  group_by(eye_color) |> # group by eye color
  summarize(total = n()) |> # make new variable called "total"
  arrange(desc(total)) #sort in descending order
```

## More resources to check out

Reporting with Data in R textbook:

* Chapter 14 in (Troubleshooting)
* Chapter 13 (R Functions)

## More tips:

* Write beautiful code
* Comment out things that didn't work
